### 2019-11-12 ty.tex
*** empty log message ***

%\newpage
\pagestyle{empty}
\chapter*{Acknowledgements}
% \begin{center}
% {\centering{\chapter*{Acknowledgements}}}
% \end{center}
\begin{quote}
% Sou grata ao Prof. Luiz Fernando Ziebell pela excelente orientação.
% Sua grande dedicação em ensinar, sua disponibilidade para solucionar
% dúvidas e sua imensa paciência foram decisivos para a execução deste
% trabalho. Também sou grata aos colegas de Grupo pela agradável convivência
% e pela constante troca de conhecimento.

% Agradeço aos amigos da ``CG''. À Amanda, à Lais e à Nicole pelas
% diversas e divertidas conversas sobre ``a vida o universo e tudo mais''.
% Ao Demétrius e ao Vinícius pelas discussões sem sentido mais engraçadas
% e irritantes que já tive.

% Reservo um agradecimento especial à minha família, que tanto me apoiou.
% Ao meu marido pelo companheirismo e incentivo. Ao meu filho por nortear 
% a minha vida e enchê-la de emoções. À minha mãe pelo amor e pela dedicação
% à minha educação. Amo vocês.
\end{quote}

>>>>

%\newpage
\pagestyle{empty}
\chapter*{Acknowledgements}
% \begin{center}
% {\centering{\chapter*{Acknowledgements}}}
% \end{center}
%\begin{quote}
To my supervisor Luiz Fernando Ziebell, whose guidance, encouragement,
and patience (tons of) made this work possible. Particularly, I would
like to state my sincere appreciation for the trusting he always
demonstrated to have in my capabilities for developing high-quality
research and for his availability to help me when I needed. Professor,
I am grateful for all these years of learning and fruitful work that
are culminating in this doctoral thesis.

To Peter Yoon, for the all the collaboration and for receiving me in
the University of Maryland. Peter, I also want to thank you for all
the encouragement in this beginning of career. That meant a lot to me.

To Dr. Adolfo Viñas who dedicated a part of his time to teach me PIC
simulation and discuss the subtleties of kinetic theory of plasmas.
Dr. Viñas, thank you very much for your time and your availability.

To my friends that never let me down. Nicole for the companionship, life

To my family for the patience, support and for always stand by me even
when I just needed to be alone to do my work. Gabriel,

%\end{quote}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
